Blockchain System

### 2020-08-18 papers/execution-model/model.tex
Add files via upload

\begin{definition}[Query]
An query is expressed as the following syntax:
\\
$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$
%$\mid$ get delegate for $\mathbf{pkh}$
\\$\mid$ get status for $\mathbf{oph}$ 
\\$\mid$ get contract storage $\mathbf{pkh}$ 
\\$\mid$ get code for $\mathbf{pkh}$ 
%\\$\mid$ waiting for $\mathbf{oph}$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\mathbf{pkh}$
\\$\mid$ get public key for $\mathbf{pkh}$
%\\$\mid$ get balance for $\mathbf{pkh}$
\\$\mid$ get counter for $\mathbf{pkh}$

@@

\section{Rules}
\subsection{Transfers}

Rule 1 [proposal]:

@@

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$}\\
\text{$\langle$[C, O, S],[($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh'$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
 \text{[P,$<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $puk'$, $n$, $m$), T, t' + 1]}}} 
\end{equation}
\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

\subsection{Smart Contracts}

\subsubsection*{A. Originate}

Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${puh}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 2 [injected]:}

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}} 
\end{equation}

\subsubsection*{Rule 3 [rejected of code]:}

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 4 [rejected of counter]:}

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 5 [rejected of balance]:}

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 6 [included]:}
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O, addContr(S, $id$, } \\
\text{generateHash($id$, $code$, $s$, t'), $code$)], [P,$<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $n$, $m$), addOrig(T, $<$ generateHash($id$, $code$, $s$, t'), $0$, $code$, } \\
 \text{getStorage($code$, $s$) $>$), t' + 1]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 7 [timeout]:}
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

\subsubsection*{B. Transfer}

\subsubsection*{Rule 1 [proposal]:}

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 2 [injected]:}

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkContr(T, $puh$, s) }}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
\text{T, t] $\rangle$}}} 
\end{equation}

\subsubsection*{Rule 3 [rejected of counter]:}

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 4 [rejected of balance]:}

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 5 [rejected of public key]:}

\begin{equation}{}
\frac{\text{$\neg$ checkContr(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 6 [rejected of argument]:}

\begin{equation}{}
\frac{\text{$\neg$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}

\subsubsection*{Rule 7 [included]:}
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
\text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
\text{updateSucc(K, puk, '', $n$, $m$), updateConstr(T, $puh$, $s$), t' + 1]}}} 
\end{equation}

\subsubsection*{Rule 8 [timeout]:}
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
\text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
\end{equation}

@@

    \item Function \verb!checkId(id, S)! checks whether a contract $id$ exists in S

@@

    \item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S

    \item Function \verb! generateOph(pkh,pkh', n, m, t)! generates a operation hash

@@

    \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
    \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
\end{enumerate}

>>>>

\begin{definition}[Query]
An query is expressed as the following syntax:
\\
$\mathbf{qry}$ ::= get balance for $\mathbf{pkh}$ $/$ $\mathbf{puh}$
%$\mid$ get delegate for $\mathbf{pkh}$
\\$\mid$ get status for $\mathbf{oph}$ 
\\$\mid$ get contract storage $\mathbf{puh}$ 
\\$\mid$ get code for $\mathbf{puh}$ 
%\\$\mid$ waiting for $\mathbf{oph}$ to be included in $\mathbf{m}$ blocks
%\\$\mid$ get timestamp
%\\$\mid$ get contracts
%\\$\mid$ show contracts for $\mathbf{pkh}$
\\$\mid$ get public key for $\mathbf{pkh}$
%\\$\mid$ get balance for $\mathbf{pkh}$
\\$\mid$ get counter for $\mathbf{pkh}$

@@

\section{Rules}
\subsection{Transfers}
\\
\\
Rule 1 [proposal]:

@@

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$}\\
\text{$\langle$[C, O, S], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh'$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(K, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ }\\
\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
 \text{[P, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $puk'$, $n$, $m$), T, t' + 1]}}} 
\end{equation}
\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}

\subsection{Smart Contracts}
\\
A. Originate
\\
\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C) $\wedge$ checkId($id$, S)}}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ \text{checkPrg($code$, $s$)}}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: O, S], [P, A, K, T, t] $\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: P, A, updateCou(K, $pkh$, True), T, t] $\rangle$}}} 
\end{equation}
\\
\\
Rule 3 [rejected of code]:

\begin{equation}{}
\frac{\text{$\neg$ checkPrg($code$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 4 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$))} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$ [C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 5 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, O, S],} \text{[P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{$\langle$[C, O, S], [$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running } \\
\text{${code}$ init ${s}$), t $>$ :: P, A, K, T, t' ]$\rangle$ $\rightarrow$ $\langle$[C, O,($<$ $id$, } \\
\text{generateHash($id$, $code$, $s$, t'), $code$ $>$ :: S)], [P, $<$ (originate contract ${id}$ } \\
\text{transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$), t' $>$ :: A, updateSucc(K, } \\
\text{$puk$, $n$, $m$), ($<$ generateHash($id$, $code$, $s$, t'), $n$, $code$, } \\
 \text{getStorage($code$, $s$) $>$) :: T), t' + 1]$\rangle$}}} 
\end{equation}
\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[$<$ (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$) $>$ } \\
\text{:: P, A, K, T, t' ] $\rightarrow$[P, A, updateCou(K, $puk$, False), T, t']}}} 
\end{equation}
\\
\\
B. \mathbf{Transfer}
\\
\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, C)  }}{\parbox{4.2in}{\text{$\langle$[C, O, S], [P, A, K, T, t]$\rangle$ $\rightarrow$ $\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ }  \\
\text{fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBan(K, $pkh$, $n$, $m$) $\wedge$ checkCou(K, $pkh$) $\wedge$ checkPuh(T, $puh$)}
\\
\text{ $\wedge$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$  $\langle$[C, O, S], [($<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), }\\
 \text{generateOph($pkh$, $puh$, $s$, $n$, $m$, t), t $>$) :: P, A, updateCou(K, $pkh$, True), }\\
\text{T, t] $\rangle$}}} 
\end{equation}
\\
\\
Rule 3 [rejected of counter]:

\begin{equation}{}
\frac{\text{$\neg$ checkCou(K, $pkh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$  }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 4 [rejected of balance]:

\begin{equation}{}
\frac{\text{$\neg$ checkBan(K, $pkh$, $n$, $m$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 5 [rejected of public hash]:

\begin{equation}{}
\frac{\text{$\neg$ checkPuh(T, $puh$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$ }\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 6 [rejected of argument]:

\begin{equation}{}
\frac{\text{$\neg$ checkArg(T, $puh$, $s$)}}{\parbox{4.2in}{\text{$\langle$[C, (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$) :: O, S], [P, A, K, T, t]$\rangle$}\\
\text{$\rightarrow$ $\langle$[C, O, S], [P, A, K, T, t]$\rangle$}}} 
\end{equation}
\\
\\
Rule 7 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puh$ fee $m$, oph, t $>$ :: P, A, K, T, t' ] $\rightarrow$ } \\
\text{[P, $<$ (transfer ${n}$ from ${pkh}$ to  ${puh}$ arg ${s}$ fee ${m}$), oph, t' $>$ :: A, } \\
\text{updateSucc(K, puk, \'\', $n$, $m$), updateConstr(T, $puh$, $n$, $s$), t' + 1]}}} 
\end{equation}
\\
Rule 8 [timeout]:
\begin{equation}{}
\frac{\text{t' - t $>=$ 60}}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, t $>$ :: P, A, K, T, t' ] $\rightarrow$} \\
\text{[P, A, updatecou(K, $puk$, False), T, t']}}} 
\end{equation}

@@

    \item Function \verb!checkId(id, S)! checks whether a contract $id$ does not already exist in S

@@

    %\item Function \verb!addContr(S, id, puh, code)! adds a new  contract $<$ $id$, $puh$, $code$ $>$  into S

    \item Function \verb! generateOph(pkh,pkh′, n, m, t)! generates a operation hash

@@

   % \item Function \verb!addOrig(T,< hash, 0, code, storage >)! add the a new originator $<$ $puh$, 0, $code$, $storage$ $>$ 
    \item Function \verb!getStorage(code, s)! gets the storage for the code $code$ and the input $s$
\end{enumerate}
